DraftOne

### 2016-07-06 writing/JSSDraft/JSSDraft.Rmd
Adding Strickland summary

>>>>

\citet{Strickland2013} used a simulation study to investigate the effects of measurement error resulting from instrument imprecision and spacial misalignment on the estimates of health effects related to ambient air pollutant concentrations.  They first used air-quality measurements obtained from several networks of monitoring stations in Atlanta to estimate various distributional properties associated with pollutant concentrations, including spatial and temporal autocorrelation. They used these estimates to generate daily two-dimensional pollutant fields for Atlanta at 5 km grids, producing "true" population-weighted average pollutant concentrations (TPWA).  They then simulated grid-specific counts of daily ED visits using TPWA as a covariate, among others.

The authors then created three different pollutant metrics based on their simulated data which contained additional measurement error and compared estimates of relative risk using these metrics to the RR = 1.05 they specified while simulating the TPWA.  As expected they found that the population-weighted average metric resulted in less bias than measurements from a single monitoring station or measurements averaged across stations.
